% !TeX spellcheck = en_US

\section{Problem 8}
ADALINE is a single-layer artificial neural network that can learn and adapt to non-linear relationships between inputs and outputs. \\
It consists of a single neuron with a linear activation function. Each input of the neuron has a corresponding weight,which is adapted during training to minimize the error between the network's output and the desired output. To adjust the weights the algorithm uses the learning rule α.
\vspace{0.3cm}

Suppose that we have the following three reference patterns and their targets:
\vspace{5mm}

\[
\begin{array}{ccc}
%	\centering
	\left\{ 
	p_1 = \left[
	\begin{array}{c}
		2 \\
		4
	\end{array}
	\right], t_1 = \left[26\right]
	\right\} & 
	\left\{ 
	p_2 = \left[
	\begin{array}{c}
		4 \\
		2
	\end{array}
	\right], t_2 = \left[26\right]
	\right\}
	&\left\{ 
	p_3 = \left[
	\begin{array}{c}
		-2 \\
		-2
	\end{array}
	\right], t_3 = \left[-26\right]
	\right\}
	
\end{array}
\]

\vspace{5mm}

The probability of vector p1 is P1 = 0.20, the probability of vector p2 is P2 = 0.70, and the probability of vector p3 is P3 = 0.10.\\

\subsection{Question a}
The number of inputs to an ADALINE network for any neural network is determined by the dimensionality of our data,not the number of patterns that we have. In our case, each pattern is a 2-dimensional vector. Therefore, our ADALINE network has two inputs, one for each dimension.\\
In an ADALINE network, the number of weights is equal to the number of inputs. In our case, each pattern is a 2-dimensional vector. Thus, our neaural network will have two weights, one for each dimension of the input.


	

